
```{r include = FALSE}
require(rmarkdown); require(knitr); require(sevenbridges); require(readr); require(jsonlite);

options(max.print = "99"); opts_knit$set(width = 99)
opts_chunk$set(cache=FALSE, tidy=FALSE)

source("~/sbg_auth.R")

```

<hr>

Wrapping of hotspot3d for use in any cwl compatible platform.

## base command

```{sh base command, eval=FALSE}

hotspot3d... [fill this out]

```

## docker 

docker file

https://github.com/teamcgc/hotspot3d/Dockerfile

The docker conatiner is

``` teamcgc/hotspot3d:latest ```

## App ports {.tabset .tabset-fade .tabset-tabs}

### Inputs

```{r inputs, eval=run.mode=="push"}
inputs = list(
  
input(id = "tar_file", label = "tar_file", description = "tar_file", type = "File", position = 1)

)

```

### Outputs

```{r output, eval = run.mode=="push"}

outputs = list(

output(id = "std_out", label = "std_out", 
description = "standard output", type = "File...",
metadata = list(org = "cgp"),
glob = Expression(engine = "#cwl-js-engine",
script = "\"*.{out}\""))
)


```

## Define Tool Object and Push to Platform {.tabset .tabset-fade .tabset-tabs}
  
### Tool object

```{r 5 create tool object, eval=run.mode=="push"}

tool <- Tool(
id = "hotspot3d",
label = "hotspot3d",
hints = requirements(docker(pull = "teamcgc/hotspot3d:latet"), cpu(1), mem(1000)),
baseCommand = "hotspot3d",
stdout = "std.out",
inputs = inputs,
outputs = outputs
)


```

### Make cwl file

```{r make cwl, eval=destination=="platform"}

write(tool$toJSON(pretty = TRUE), "hotspot3d_cwl.json")

```

### Push app to sbg platform

```{r push app to sbg, eval=destination=="platform"}

project$app_add("hotspot3d", tool)


```


### Notes

These columns are required

Hugo_Symbol

Chromosome

Start_Position

End_Position

Variant_Classification

Reference_Allele

Tumor_Seq_Allele1

Tumor_Seq_Allele2

Tumor_Sample_Barcode

with 2 non-standard columns:

a transcript ID column

a protein peptide change column (HGVS p. single letter abbreviations, ie p.T790M)

